BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2016-12-28 Paper2/BOAST.tex
section related work

  \subsection{Application Auto-Tuning}

  The most convenient way to obtain an application that can be auto-tuned on a
given platform is to base this application on a widely used computing library.
BLAS~\cite{dongarra1990set} and LAPACK~\cite{laug} are such libraries. These
libraries are either hand tuned for selected platforms or have auto-tuned
implementations. Atlas~\cite{whaley04} is an auto-tuned implementation of
BLAS/LAPACK. ATLAS authors defined the \emph{Automated Empirical Optimization of
Software} methodology that we implemented with BOAST. Their kernel generation is
done using macro-functions in C.

  Nonetheless many application formalisms cannot be reduced to standardized
library or border on what could be considered edge cases for those libraries and
not as optimized as more general cases. Orio~\cite{Hart2009:Orio} is an
auto-tuning framework that has an approach close of that of BOAST but they are
based on an annotated DSL describing loop transformation rather than a more
generic EDSL. Halide~\cite{ragan2013halide} is an auto-tuning framework
dedicated to image processing. It can also be used to describe other
operations on memory buffers. Those two frameworks propose automated search
space exploration to find the best version of a kernel.
LGen~\cite{spampinato2014basic} is a compiler that generates linear algebra
programs for small fixed size problems. Knowing the problem size it fully
unrolls and vectorizes loops, yielding better performance than state of the
art generic implementations.

  \subsection{Kernel Description DSL}

@@

  \subsection{Optimization Space Pruner}

@@

\section{Conclusion and Future Works}

>>>>

%%% APPLICATION AUTO-TUNING %%%
\subsection{Application Auto-Tuning}

The most convenient way to obtain an application that can be auto-tuned on a
given platform is to base this application on a widely used computing library.
BLAS~\cite{dongarra1990set} and LAPACK~\cite{laug} are such libraries. These
libraries are either hand tuned for selected platforms or have auto-tuned
implementations. Atlas~\cite{whaley04} is an auto-tuned implementation of
BLAS/LAPACK. ATLAS authors defined the \emph{Automated Empirical Optimization of
Software} methodology that we implemented with BOAST. Their kernel generation is
performed using macro-functions in C.

Nonetheless many application formalisms cannot be reduced to standardized
library or border on what could be considered edge cases for those libraries and
not as optimized as more general cases. Orio~\cite{Hart2009:Orio} is an
auto-tuning framework that has an approach close of that of BOAST but they are
based on an annotated DSL describing loop transformations rather than a more
generic EDSL. Halide~\cite{ragan2013halide} is an auto-tuning framework
dedicated to image processing. It can also be used to describe other
operations on memory buffers. Those two frameworks propose automated search
space exploration to find the best version of a kernel.
LGen~\cite{spampinato2014basic} is a compiler that generates linear algebra
programs for small fixed size problems. Knowing the problem size, it fully
unrolls and vectorizes loops, yielding better performance than state of the
art generic implementations.

%%% KERNEL DESCRIPTION DSL %%%
\subsection{Kernel Description DSL}

@@

%%% OPTIMIZATION SPACE PRUNER %%%
\subsection{Optimization Space Pruners}

@@

%%% Conclusion and Future Works %%%
\section{Conclusion and Future Works}
